### 2025-03-07 paper/preprint/paper.tex
more work on app

\usepackage{arxiv}
\usepackage{orcidlink}
\usepackage{amsmath}
\usepackage[T1]{fontenc}
\usepackage{placeins}
\makeatletter
\@ifpackageloaded{tcolorbox}{}{\usepackage[skins,breakable]{tcolorbox}}
\@ifpackageloaded{fontawesome5}{}{\usepackage{fontawesome5}}
\definecolor{quarto-callout-color}{HTML}{909090}
\definecolor{quarto-callout-note-color}{HTML}{0758E5}
\definecolor{quarto-callout-important-color}{HTML}{CC1914}
\definecolor{quarto-callout-warning-color}{HTML}{EB9113}
\definecolor{quarto-callout-tip-color}{HTML}{00A047}
\definecolor{quarto-callout-caution-color}{HTML}{FC5300}
\definecolor{quarto-callout-color-frame}{HTML}{acacac}
\definecolor{quarto-callout-note-color-frame}{HTML}{4582ec}
\definecolor{quarto-callout-important-color-frame}{HTML}{d9534f}
\definecolor{quarto-callout-warning-color-frame}{HTML}{f0ad4e}
\definecolor{quarto-callout-tip-color-frame}{HTML}{02b875}
\definecolor{quarto-callout-caution-color-frame}{HTML}{fd7e14}
\makeatother
\makeatletter
\@ifpackageloaded{caption}{}{\usepackage{caption}}
\AtBeginDocument{%
\ifdefined\contentsname
  \renewcommand*\contentsname{Table of contents}
\else
  \newcommand\contentsname{Table of contents}
\fi
\ifdefined\listfigurename
  \renewcommand*\listfigurename{List of Figures}
\else
  \newcommand\listfigurename{List of Figures}
\fi
\ifdefined\listtablename
  \renewcommand*\listtablename{List of Tables}
\else
  \newcommand\listtablename{List of Tables}
\fi
\ifdefined\figurename
  \renewcommand*\figurename{Figure}
\else
  \newcommand\figurename{Figure}
\fi
\ifdefined\tablename
  \renewcommand*\tablename{Table}
\else
  \newcommand\tablename{Table}
\fi
}
\@ifpackageloaded{float}{}{\usepackage{float}}
\floatstyle{ruled}
\@ifundefined{c@chapter}{\newfloat{codelisting}{h}{lop}}{\newfloat{codelisting}{h}{lop}[chapter]}
\floatname{codelisting}{Listing}
\newcommand*\listoflistings{\listof{codelisting}{List of Listings}}
\usepackage{amsthm}
\theoremstyle{definition}
\newtheorem{definition}{Definition}[section]
\theoremstyle{plain}
\newtheorem{proposition}{Proposition}[section]
\theoremstyle{definition}
\newtheorem{example}{Example}[section]
\theoremstyle{plain}
\newtheorem{corollary}{Research Question}[section]
\theoremstyle{remark}
\AtBeginDocument{\renewcommand*{\proofname}{Proof}}
\newtheorem*{remark}{Remark}
\newtheorem*{solution}{Solution}
\newtheorem{refremark}{Remark}[section]
\newtheorem{refsolution}{Solution}[section]
\makeatother
\makeatletter
\makeatother
\makeatletter
\@ifpackageloaded{caption}{}{\usepackage{caption}}
\@ifpackageloaded{subcaption}{}{\usepackage{subcaption}}
\makeatother
\newcounter{quartocalloutnteno}
\newcommand{\quartocalloutnte}[1]{\refstepcounter{quartocalloutnteno}\label{#1}}

@@

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\tightlist
\item
  Limited to classification models.
\item
  Proxy attributes of immutable features.
\item
  Increased training time.
\item
  Training instabilities
\item
  Fairness and caveats (aware it's not a classical approach in this
  context, but there is a clear link).
\end{enumerate}

@@

\begin{tcolorbox}[enhanced jigsaw, colback=white, colframe=quarto-callout-note-color-frame, left=2mm, coltitle=black, toptitle=1mm, breakable, bottomtitle=1mm, opacitybacktitle=0.6, leftrule=.75mm, colbacktitle=quarto-callout-note-color!10!white, title={Note}, titlerule=0mm, arc=.35mm, toprule=.15mm, rightrule=.15mm, opacityback=0, bottomrule=.15mm]

@@

\begin{tcolorbox}[enhanced jigsaw, colback=white, colframe=quarto-callout-note-color-frame, left=2mm, coltitle=black, toptitle=1mm, breakable, bottomtitle=1mm, opacitybacktitle=0.6, leftrule=.75mm, colbacktitle=quarto-callout-note-color!10!white, title={Note \ref*{nte-gen-params-final-run-train}: Training Phase}, titlerule=0mm, arc=.35mm, toprule=.15mm, rightrule=.15mm, opacityback=0, bottomrule=.15mm]

@@

\begin{tcolorbox}[enhanced jigsaw, colback=white, colframe=quarto-callout-note-color-frame, left=2mm, coltitle=black, toptitle=1mm, breakable, bottomtitle=1mm, opacitybacktitle=0.6, leftrule=.75mm, colbacktitle=quarto-callout-note-color!10!white, title={Note \ref*{nte-gen-params-final-run-eval}: Evaluation Phase}, titlerule=0mm, arc=.35mm, toprule=.15mm, rightrule=.15mm, opacityback=0, bottomrule=.15mm]

@@

\begin{tcolorbox}[enhanced jigsaw, colback=white, colframe=quarto-callout-note-color-frame, left=2mm, coltitle=black, toptitle=1mm, breakable, bottomtitle=1mm, opacitybacktitle=0.6, leftrule=.75mm, colbacktitle=quarto-callout-note-color!10!white, title={Note \ref*{nte-pen-final-run-train}: Training Phase}, titlerule=0mm, arc=.35mm, toprule=.15mm, rightrule=.15mm, opacityback=0, bottomrule=.15mm]

@@

\begin{tcolorbox}[enhanced jigsaw, colback=white, colframe=quarto-callout-note-color-frame, left=2mm, coltitle=black, toptitle=1mm, breakable, bottomtitle=1mm, opacitybacktitle=0.6, leftrule=.75mm, colbacktitle=quarto-callout-note-color!10!white, title={Note \ref*{nte-pen-final-run-eval}: Evaluation Phase}, titlerule=0mm, arc=.35mm, toprule=.15mm, rightrule=.15mm, opacityback=0, bottomrule=.15mm]

@@

>>>>

\usepackage{arxiv}
\usepackage{orcidlink}
\usepackage{amsmath}
\usepackage[T1]{fontenc}
\usepackage{placeins}
\makeatletter
\@ifpackageloaded{tcolorbox}{}{\usepackage[skins,breakable]{tcolorbox}}
\@ifpackageloaded{fontawesome5}{}{\usepackage{fontawesome5}}
\definecolor{quarto-callout-color}{HTML}{909090}
\definecolor{quarto-callout-note-color}{HTML}{0758E5}
\definecolor{quarto-callout-important-color}{HTML}{CC1914}
\definecolor{quarto-callout-warning-color}{HTML}{EB9113}
\definecolor{quarto-callout-tip-color}{HTML}{00A047}
\definecolor{quarto-callout-caution-color}{HTML}{FC5300}
\definecolor{quarto-callout-color-frame}{HTML}{acacac}
\definecolor{quarto-callout-note-color-frame}{HTML}{4582ec}
\definecolor{quarto-callout-important-color-frame}{HTML}{d9534f}
\definecolor{quarto-callout-warning-color-frame}{HTML}{f0ad4e}
\definecolor{quarto-callout-tip-color-frame}{HTML}{02b875}
\definecolor{quarto-callout-caution-color-frame}{HTML}{fd7e14}
\makeatother
\makeatletter
\@ifpackageloaded{caption}{}{\usepackage{caption}}
\AtBeginDocument{%
\ifdefined\contentsname
  \renewcommand*\contentsname{Table of contents}
\else
  \newcommand\contentsname{Table of contents}
\fi
\ifdefined\listfigurename
  \renewcommand*\listfigurename{List of Figures}
\else
  \newcommand\listfigurename{List of Figures}
\fi
\ifdefined\listtablename
  \renewcommand*\listtablename{List of Tables}
\else
  \newcommand\listtablename{List of Tables}
\fi
\ifdefined\figurename
  \renewcommand*\figurename{Figure}
\else
  \newcommand\figurename{Figure}
\fi
\ifdefined\tablename
  \renewcommand*\tablename{Table}
\else
  \newcommand\tablename{Table}
\fi
}
\@ifpackageloaded{float}{}{\usepackage{float}}
\floatstyle{ruled}
\@ifundefined{c@chapter}{\newfloat{codelisting}{h}{lop}}{\newfloat{codelisting}{h}{lop}[chapter]}
\floatname{codelisting}{Listing}
\newcommand*\listoflistings{\listof{codelisting}{List of Listings}}
\usepackage{amsthm}
\theoremstyle{plain}
\newtheorem{corollary}{Research Question}[section]
\theoremstyle{plain}
\newtheorem{proposition}{Proposition}[section]
\theoremstyle{definition}
\newtheorem{definition}{Definition}[section]
\theoremstyle{definition}
\newtheorem{example}{Example}[section]
\theoremstyle{remark}
\AtBeginDocument{\renewcommand*{\proofname}{Proof}}
\newtheorem*{remark}{Remark}
\newtheorem*{solution}{Solution}
\newtheorem{refremark}{Remark}[section]
\newtheorem{refsolution}{Solution}[section]
\makeatother
\makeatletter
\makeatother
\makeatletter
\@ifpackageloaded{caption}{}{\usepackage{caption}}
\@ifpackageloaded{subcaption}{}{\usepackage{subcaption}}
\makeatother
\newcounter{quartocalloutnteno}
\newcommand{\quartocalloutnte}[1]{\refstepcounter{quartocalloutnteno}\label{#1}}

@@

\subsection{Approach/Future Directions}\label{approachfuture-directions}

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\tightlist
\item
  Limited to classification models.
\item
  Training instabilities.
\item
  Hyperparameter sensitivity -\textgreater{} can we do better than grid
  search? (Bayes opt, \ldots)
\end{enumerate}

\subsection{Limitations}\label{limitations}

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\setcounter{enumi}{2}
\tightlist
\item
  Proxy attributes of immutable features.
\item
  Increased training time.
\item
  Fairness and caveats (aware it's not a classical approach in this
  context, but there is a clear link).
\end{enumerate}

@@

\begin{tcolorbox}[enhanced jigsaw, colbacktitle=quarto-callout-note-color!10!white, colback=white, breakable, left=2mm, coltitle=black, rightrule=.15mm, bottomtitle=1mm, toprule=.15mm, toptitle=1mm, titlerule=0mm, arc=.35mm, colframe=quarto-callout-note-color-frame, bottomrule=.15mm, opacitybacktitle=0.6, title={Note}, opacityback=0, leftrule=.75mm]

@@

\begin{tcolorbox}[enhanced jigsaw, colbacktitle=quarto-callout-note-color!10!white, colback=white, breakable, left=2mm, coltitle=black, rightrule=.15mm, bottomtitle=1mm, toprule=.15mm, toptitle=1mm, titlerule=0mm, arc=.35mm, colframe=quarto-callout-note-color-frame, bottomrule=.15mm, opacitybacktitle=0.6, title={Note \ref*{nte-gen-params-final-run-train}: Training Phase}, opacityback=0, leftrule=.75mm]

@@

\begin{tcolorbox}[enhanced jigsaw, colbacktitle=quarto-callout-note-color!10!white, colback=white, breakable, left=2mm, coltitle=black, rightrule=.15mm, bottomtitle=1mm, toprule=.15mm, toptitle=1mm, titlerule=0mm, arc=.35mm, colframe=quarto-callout-note-color-frame, bottomrule=.15mm, opacitybacktitle=0.6, title={Note \ref*{nte-gen-params-final-run-eval}: Evaluation Phase}, opacityback=0, leftrule=.75mm]

@@

\begin{tcolorbox}[enhanced jigsaw, colbacktitle=quarto-callout-note-color!10!white, colback=white, breakable, left=2mm, coltitle=black, rightrule=.15mm, bottomtitle=1mm, toprule=.15mm, toptitle=1mm, titlerule=0mm, arc=.35mm, colframe=quarto-callout-note-color-frame, bottomrule=.15mm, opacitybacktitle=0.6, title={Note \ref*{nte-pen-final-run-train}: Training Phase}, opacityback=0, leftrule=.75mm]

@@

\begin{tcolorbox}[enhanced jigsaw, colbacktitle=quarto-callout-note-color!10!white, colback=white, breakable, left=2mm, coltitle=black, rightrule=.15mm, bottomtitle=1mm, toprule=.15mm, toptitle=1mm, titlerule=0mm, arc=.35mm, colframe=quarto-callout-note-color-frame, bottomrule=.15mm, opacitybacktitle=0.6, title={Note \ref*{nte-pen-final-run-eval}: Evaluation Phase}, opacityback=0, leftrule=.75mm]

@@

\subsubsection{Training Parameters}\label{training-parameters}

The hyperparameter grid with other varying training parameters is shown
in Note~\ref{nte-train-final-run-train}. The corresponding evaluation
grid used for these experiments is shown in
Note~\ref{nte-train-final-run-eval}.

\begin{tcolorbox}[enhanced jigsaw, colbacktitle=quarto-callout-note-color!10!white, colback=white, breakable, left=2mm, coltitle=black, rightrule=.15mm, bottomtitle=1mm, toprule=.15mm, toptitle=1mm, titlerule=0mm, arc=.35mm, colframe=quarto-callout-note-color-frame, bottomrule=.15mm, opacitybacktitle=0.6, title={Note \ref*{nte-train-final-run-train}: Training Phase}, opacityback=0, leftrule=.75mm]

\quartocalloutnte{nte-train-final-run-train}

  \begin{itemize}
  \tightlist
  \item
    Burnin: \texttt{0.0,\ 0.5}
  \item
    No.~Counterfactuals: \texttt{100,\ 1000}
  \item
    No.~Epochs: \texttt{50,\ 100}
  \item
    Objective: \texttt{full,\ vanilla}
  \end{itemize}
\end{itemize}

\begin{tcolorbox}[enhanced jigsaw, colbacktitle=quarto-callout-note-color!10!white, colback=white, breakable, left=2mm, coltitle=black, rightrule=.15mm, bottomtitle=1mm, toprule=.15mm, toptitle=1mm, titlerule=0mm, arc=.35mm, colframe=quarto-callout-note-color-frame, bottomrule=.15mm, opacitybacktitle=0.6, title={Note \ref*{nte-train-final-run-eval}: Evaluation Phase}, opacityback=0, leftrule=.75mm]

\quartocalloutnte{nte-train-final-run-eval}

\paragraph{Plausibility}\label{plausibility-3}

The results with respect to the plausibility measure are shown in
Figure~\ref{fig-grid-train-plaus-circles} to
Figure~\ref{fig-grid-train-plaus-over}.

\pandocbounded{\includegraphics[keepaspectratio]{../../paper/experiments/output/final_run/training_params/mlp/circles/evaluation/results/ce/burnin---nce---nepochs---burnin---burnin/plausibility_distance_from_target.png}}

\caption{\label{fig-grid-train-plaus-circles}Average outcomes for the
plausibility measure across hyperparameters. Data: Circles.}

\pandocbounded{\includegraphics[keepaspectratio]{../../paper/experiments/output/final_run/training_params/mlp/lin_sep/evaluation/results/ce/burnin---nce---nepochs---burnin---burnin/plausibility_distance_from_target.png}}

\caption{\label{fig-grid-train-plaus-lin_sep}Average outcomes for the
plausibility measure across hyperparameters. Data: Linearly Separable.}

\pandocbounded{\includegraphics[keepaspectratio]{../../paper/experiments/output/final_run/training_params/mlp/moons/evaluation/results/ce/burnin---nce---nepochs---burnin---burnin/plausibility_distance_from_target.png}}

\caption{\label{fig-grid-train-plaus-moons}Average outcomes for the
plausibility measure across hyperparameters. Data: Moons.}

\pandocbounded{\includegraphics[keepaspectratio]{../../paper/experiments/output/final_run/training_params/mlp/over/evaluation/results/ce/burnin---nce---nepochs---burnin---burnin/plausibility_distance_from_target.png}}

\caption{\label{fig-grid-train-plaus-over}Average outcomes for the
plausibility measure across hyperparameters. Data: Overlapping.}

\paragraph{Cost}\label{cost-2}

The results with respect to the cost measure are shown in
Figure~\ref{fig-grid-train-cost-circles} to
Figure~\ref{fig-grid-train-cost-over}.

\pandocbounded{\includegraphics[keepaspectratio]{../../paper/experiments/output/final_run/training_params/mlp/circles/evaluation/results/ce/burnin---nce---nepochs---burnin---burnin/distance.png}}

\caption{\label{fig-grid-train-cost-circles}Average outcomes for the
cost measure across hyperparameters. Data: Circles.}

\pandocbounded{\includegraphics[keepaspectratio]{../../paper/experiments/output/final_run/training_params/mlp/lin_sep/evaluation/results/ce/burnin---nce---nepochs---burnin---burnin/distance.png}}

\caption{\label{fig-grid-train-cost-lin_sep}Average outcomes for the
cost measure across hyperparameters. Data: Linearly Separable.}

\pandocbounded{\includegraphics[keepaspectratio]{../../paper/experiments/output/final_run/training_params/mlp/moons/evaluation/results/ce/burnin---nce---nepochs---burnin---burnin/distance.png}}

\caption{\label{fig-grid-train-cost-moons}Average outcomes for the cost
measure across hyperparameters. Data: Moons.}

\pandocbounded{\includegraphics[keepaspectratio]{../../paper/experiments/output/final_run/training_params/mlp/over/evaluation/results/ce/burnin---nce---nepochs---burnin---burnin/distance.png}}

\caption{\label{fig-grid-train-cost-over}Average outcomes for the cost
measure across hyperparameters. Data: Overlapping.}

### 2025-03-07 paper/sections/other/grids.qmd
more work on app

>>>>

### Training Parameters

```{julia}
grid_dir = joinpath(res_dir, "training_params/mlp")
data_dirs = readdir(grid_dir) |> x -> joinpath.(grid_dir, x) |> x -> x[isdir.(x)]
data_names = basename.(data_dirs)
suffix = "evaluation/results/ce/burnin---nce---nepochs---burnin---burnin/"
```

The hyperparameter grid with other varying training parameters is shown in @nte-train-final-run-train. The corresponding evaluation grid used for these experiments is shown in @nte-train-final-run-eval.

::: {#nte-train-final-run-train .callout-note}

::: {#nte-train-final-run-eval .callout-note}

fig_label_prefix = "grid-train-plaus"
fig_labels = (nm -> "fig-$(fig_label_prefix)-$nm").(data_names)
_str = "The results with respect to the plausibility measure are shown in @$(fig_labels[1]) to @$(fig_labels[end])."
println(_str)
```

fig_label_prefix = "grid-train-cost"
fig_labels = (nm -> "fig-$(fig_label_prefix)-$nm").(data_names)
_str = "The results with respect to the cost measure are shown in @$(fig_labels[1]) to @$(fig_labels[end])."
println(_str)
```
